---
title: <center> ECS 132 Fall 2020, Project</center>
header-includes:
- \usepackage{tikz}
- \usepackage{amsmath}
- \usepackage{graphicx}
- \usepackage{fancyhdr}
- \usepackage{geometry}
- \usepackage{float}
- \usepackage{xcolor}
date: "<center> December 1, 2020 </center>"
output:
  html_document:
    
    highlight: tango
    number_sections: yes
    theme: united
    toc: no
    toc_depth: 3
    pandoc_args:
    - --number-sections
    - --number-offset=2
  pdf_document:
    toc: no
    toc_depth: '3'
    highlight: tango
    number_sections: yes
---


\pagestyle{fancy}
\fancyhf{}
\rhead{Project}
\lhead{ECS 132 Fall 2020}
\rfoot{Page \thepage}

<!-- regular html comment --> 
```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
```
## Your name: Nicholas Treynor  <!-- write your name --> {-}

## Partner's name: James Lemkin   <!-- write your name --> {-}

## Any other collaborator(s):   <!-- write your name --> {-}


# Instructions {-}

1. Please refer to "ECS_132_Project.pdf" for details.

2. You may in no circumstances upload your project to private tutoring websites such as CourseHero or Chegg. Remember all material related to this course  is a property of the University of California and posting them is a violation of the copyright laws. 
    
3. If you refer to a source (either a book or the internet), you must cite it.
    
4. You may work in groups of size of at most 2. If you collaborate with others,  you must list their names.
    
5. Write your answers in R Markdown and submit the knitted pdf on Gradescope; for due date and other details see the Homework Policy and Schedule.

\setcounter{section}{2}
# Design

## 

Alice and Bob decide to use the following modulation scheme to map the bits to the inter-packet delay. A delay of $0.25$ is used to encode a bit $0$ and delay of $0.75$ is used to encode a bit $1$. Write a short R code  that will generate the modified packet stream that contains the secret message.

charToRaw(x) - converts characters to hexadecimal value
rawToBits(x) - converts hexadecimal value to bit values. The bits are in reverse order per decimal value, so the letter t corresponds to 74 in hexadecimal -> 01110100 in reality, but will return as 00101110 when using the function.

## Answer {-}

We want to output “this is a secret message”.
To do so, we need to convert the message into binary, and then send along the individual bits that make up the binary using the encoding delays. 

We need to loop over the generated strings carefully, stepping 16 forward then looping backwards over 8 integers.
```{r }
#  your R code here
message = "this is a secret message"
rawMessage = charToRaw(message)
bits = rawToBits(rawMessage)

bitLength = (nchar(message) * 8)
sentPacketsTime = numeric(bitLength + 1)
sentPacketsStream = numeric(bitLength)
sentPacketsDelays = numeric(bitLength)
currTime = 0
index = 2
for (i in 1:nchar(message)) {
  for (x in 0:7) {
    if (bits[(i*8) - x] == 00){
      sentPacketsTime[index] = currTime + 0.25
      currTime = currTime + 0.25
      sentPacketsStream[index-1] = 0
      sentPacketsDelays[index-1] = 0.25
    } else {
      sentPacketsTime[index] = currTime + 0.75
      currTime = currTime + 0.75
      sentPacketsStream[index-1] = 1
      sentPacketsDelays[index-1] = 0.75
    }
    index = index + 1
  }
}

print(sentPacketsStream)
print(sentPacketsStream)
```

## 

Plot the histogram of the inter-packet delays of the overt packet stream. Plot the histogram of the covert packet stream. Will Eve be suspicious?

## Answer {-}

```{r }
#  your R code here
data <- read.csv("Traffic_data_orig.csv", header=TRUE)
overtPacketStream = data[,2]
x = length(overtPacketStream)
overtPacketsDelays = numeric(x-1)
currTime = 0
index = 2
for (i in 2:x-1){
  overtPacketsDelays[i-1] = overtPacketStream[i]-overtPacketStream[i-1]
}

hist(overtPacketsDelays, main = "Histogram of Overt Packet Delays")
hist(sentPacketsDelays, main = "Histogram of Covert Packet Delays")
```
There is a very clear difference in the two histograms, indicating that some sort of unusual data transmission is occurring. Eve would be suspicious if she were monitoring our packet delays.

<!-- text comments here -->


## 

Alice and Bob decide to use the following modulation scheme. Let $m$, $min$, and $max$ denote the median, min, and max of the inter-packet delay of the overt packet stream. If Alice needs to send a $0$ she randomly generates a delay between $min$ and $m$. If she want to send a $1$ she randomly generates a delay between $m$ and $max$. First, compute $m$, $min$,  and $max$. Next, modify the code  in  Question 1, to generate  the packet stream that contains  the secret message.


## Answer {-}

```{r }
#  your R code here

```



## 

Plot the histogram  of the inter-packet  delays of the overt packet stream and that of the new covert packet stream. Do you think Eve will be suspicious?
  
## Answer {-}

```{r }
#  your R code here

```

<!-- text comments here -->

##  

Answer the following questions briefly (in 1 or 2 sentences)

1. How can you improve upon the method in Question 3? 

   \textbf{Answer: } <!-- enter your answer here --> 

2. We assumed the Alice will buffer up the packets and we mentioned that it was unrealistic. Why?
 
   \textbf{Answer: } <!-- enter your answer here -->

3. We have assumed that the network does not alter the inter-packet delays. What would be the problem if it did? Can you suggest methods to mitigate the effect of the changes of the inter-packet delay (noise)?

   \textbf{Answer: } <!-- enter your answer here -->


## Answer {-}

<!-- enter your answer below -->


# Implementation


## 
For  buffer size $B=20$ we want to find out the probability of overflow  and  underflow, when the IPD follows the Exponential with $\lambda =1$ pkts/sec and $i=2, 6, 10, 14, 18$. Use message size $m = 16, 32$ bits. Tabulate the results. Remember that to determine the probability you need to run multiple (say 500) experiments for each parameter, i.e., for $B = 20, m = 16, i = 2$ run $500$ experiments  and determine the probability of overflow and underflow. Similarly for other values of $i$ and $m$.

## Answer {-}


```{r }
#  your R simulation code here 


# tabulate results and compute the probabilities

```

## 
For  buffer size $B=20$ we want to find out the probability of overflow  and  underflow, when the IPD follows the Uniform distribution in the range (0,1)  and $i=2, 6, 10, 14, 18$. Use message size $m = 16, 32$ bits.  Tabulate the results. Remember that to determine the probability you need to run multiple (say 500) experiments for each parameter, i.e., for $B = 20, m = 16, i = 2$ run $500$ experiments  and determine the probability of overflow and underflow. Similarly for other values of $i$ and $m$.

## Answer {-}


```{r }
#  your R simulation code here 


# tabulate results and compute the probabilities

```

##  
Propose methods to deal with buffer overflow and underflow.


## Answer {-}

<!-- enter your answer below -->

